From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-04-19 article/article.tex
MNinor article changes
Added an indexer for distributed louvain

A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy from the social sciences \cite{fortunato2010community}.
Many algorithms exist to solve this problem, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
This approach also allows the expansion of labels to find potentially related vertices to an initial starting subset.

@@

Formally, given the partition space $\mathcal{P}$ and a query set $S$ we consider the distribution of quality scores as $\mu_i(S - i)$, for all $i$ in $S$.
In order for $S$ to be a high quality query set, its value of internal vertices should be significantly higher than for external vertices.
Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.01$.
In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.

>>>>

A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy from the social sciences \cite{fortunato2010community}.
Many algorithms exist to solve this problem, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to meaedsure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
This approach also allows the expansion of labels to find potentially related vertices to an initial starting subset.

@@

Formally, given the partition space $\mathcal{P}$ and a query set $S$ we consider the distribution of quality scores as $\mu_i(S - i)$, for all $i$ in $S$.
In order for $S$ to be a high quality query set, its value of internal vertices should be significantly higher than for external vertices.
Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.001$.
In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.
